Genome-wide changes in expression during inflorescence architecture development

### 2015-09-25 ms.Rmd
try MADS tree with genes with padj = NA removed

| **Figure**: Similarity tree of MADS proteins with L2FC values between comparable samples (and dN/dS values?) for each one:
| **rice**: rachis meristem vs. spikelet merisem.
| **arapidospis**: inflorescence meristem vs. floret meristem.
| **tomato**: simpodial meristem vs. floret meristem.

@@

@@

**`r I(pasteLabel("Figure ", figCount, "f_madsTree"))`**. Neighbour-joining similarity tree of putatative MIKC proteins in *A. thaliana*, *Solanum lycopersicum* and *Oryza sativa* ssp. *japonica*. Named proteins starting with AT_ or OS_ are from Arabidopsis or rice respectively, with synonyms in parentheses, and other proteins are labelled with their unique identifiers. The colour of the label represents the Log~2~-fold change (L~2~FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. A white background indicates that no results were returned by `DESeq2` for the gene in question, *e.g.* because of low read counts or an extreme count outlier. For rice, L~2~FC was estimated from the RM and SM samples reported here. For *A. thaliana*, L~2~FC was estimated using the inflorescence meristem and floret meristem samples reported by @Mantegazza:2014di. The simpodial meristem and floret meristem samples generated by @Park:2012dg were used to estimate L~2~FC values for tomato genes. Clades are labelled following the nomenclature presented by (**ref: Arora paper**).

>>>>

| **Figure**: Similarity tree of MADS proteins with L2FC values between comparable samples (and dN/dS values?) for each one:
| **rice**: rachis meristem vs. spikelet merisem.
| **arapidospis**: inflorescence meristem vs. floret meristem.
| **tomato**: sympodial IM vs. floret meristem.

@@

```{r f_alogFamily, fig.width = 6.614}
print(f_alogFamily)
```

**`r I(pasteLabel("Figure ", figCount, "f_mfuzzClusters"))`**. Expression of the rice G1 (ALOG) family in inflorescence meristems. Points for are plotted in red if the gene was detected in that sample or in blue otherwise. Three G1 genes, *G1L1*, *G1L2* and *G1L5* (*TAWAWA*) are expressed, and they share a similar pattern of expression.

@@

**`r I(pasteLabel("Figure ", figCount, "f_madsTree"))`**. Neighbour-joining similarity tree of putatative MIKC proteins in *A. thaliana*, *Solanum lycopersicum* and *Oryza sativa* ssp. *japonica*. Named proteins starting with AT_ or OS_ are from Arabidopsis or rice respectively, with synonyms in parentheses, and other proteins are labelled with their unique identifiers. The colour of the label represents the Log~2~-fold change (L~2~FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. A white background indicates that no results were returned by `DESeq2` for the gene in question, *e.g.* because of low read counts or an extreme count outlier. For rice, L~2~FC was estimated from the RM and SM samples reported here. For *A. thaliana*, L~2~FC was estimated using the inflorescence meristem and floret meristem samples reported by @Mantegazza:2014di. The sympodial inflorescence meristem and floret meristem samples generated by @Park:2012dg were used to estimate L~2~FC values for tomato genes. Clades are labelled following the nomenclature presented by (**ref: Arora paper**).
